Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-04 LatexNotes/Notes.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{Hist2}
\caption{Sensitivity to changes in $D_0$.
Left: Downstream histogram with $D_0 = 0.6$ (same as in Fig.~\ref{Hist1}). Right: Same with $D_0 = 0.4$. Notice the histogram changes significantly.
}
\label{Hist2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
%Notice that even though the depth ratio changes only slightly, the histograms change significantly. The upstream histograms do not depend on $D_0$ and are therefore not shown.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{Hist3}
\caption{Sensitivity to changes in the energy $E_0$.
Left: Downstream histogram with $E_0 = 1$ (same as in Fig.~\ref{Hist1}). Right: Same with $E_0 = 4$. Notice a slight change in the histogram.}
\label{Hist3}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
 %Notice that the energy changes substantially, but the histograms change only slightly. While the upstream histogram ostensible depends on $E_0$, the changes are nearly imperceptible and therefore not shown.

@@

Now, figures \ref{thetaplot}--\ref{match_micro} show results obtained by satisfying the matching condition \eqref{statmatch} using the algorithm described in \ref{sec_match}. In these tests, I use $\Lambda = 8$ and the provisional number of samples is $10^8$ (the number of accepted samples will be much lower). First, Fig.~\ref{thetaplot} shows, for given values of $\theta^-$, the corresponding values of $\theta^+$ as determined by the matching condition. For one, $\theta^- = 0$ corresponds to $\theta^+ = 0$ which is a good sanity check. Second, notice that the signs of $\theta^-$ and $\theta^+$ always agree, which is a good thing. The relationship is not a simply linear one, as the curvature is significant.

@@

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{Hist2}
\caption{Sensitivity to changes in $D_0$.
Left: Downstream histogram with $D_0 = 0.6$ (same as in Fig.~\ref{Hist1}). Right: Same with $D_0 = 0.4$. Notice the histogram changes significantly.
}
\label{Hist2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}[p]%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{Hist3}
\caption{Sensitivity to changes in the energy $E_0$.
Left: Downstream histogram with $E_0 = 1$ (same as in Fig.~\ref{Hist1}). Right: Same with $E_0 = 4$. Notice a slight change in the histogram.}
\label{Hist3}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^

@@

Now, figures \ref{thetaplot}--\ref{match_micro} show results obtained by satisfying the matching condition \eqref{statmatch} using the algorithm described in \ref{sec_match}. In these tests, we use $\Lambda = 8$ and the provisional number of samples is $10^8$ (the number of accepted samples will be much lower). We also fix $E_0 = 4$ and $D_0 = 0.5$.

First, Fig.~\ref{thetaplot} shows, for given values of $\theta^-$, the corresponding values of $\theta^+$ as determined by the matching condition. For one, $\theta^- = 0$ corresponds to $\theta^+ = 0$ which is a good sanity check. Second, notice that the signs of $\theta^-$ and $\theta^+$ always agree, which is a good thing. The relationship is not a simply linear one, as the curvature is significant.

@@

We remark that simulations have been performed with larger values of $\Lambda$, for example $\Lambda = 16$ and 20. For the provisional number of samples fixed, increasing $\Lambda$ does not drastically increase the computational time. However, the main downside to increasing $\Lambda$ is that the acceptance rate for the Gibbs distributions is substantially smaller, and therefore the statistics are less resolved.
